---
title: "Personal Loan Campaign using Logistic Regression"
output:
  word_document: default
  html_notebook: default
---


## Setting working directory and reading the csv file
```{r}
setwd("F:/DataScience/BLOG/LogRegproject1")

loanorg <- read.csv("PLXSELL.csv")
```


#View the dataset
```{r}
View (loanorg)
dim(loanorg)
str(loanorg)
names(loanorg)


```

#dataset clean up and preparation
```{r}
##remove unwanted columns CUST_ID and random
loancamp <- loanorg[,-c(1,40)]
#str(loancamp)

## remove columns AGE_BKT (similar column 'AGE' is available) and ACC_OP_DATE ##(similar column 'LEN_OF_RLTN_IN_MNTH' is available )

loancamp$AGE_BKT <- NULL
loancamp$ACC_OP_DATE <- NULL


## Convert variables into correct datatypes (FLG_HAS_CC, FLG_HAS_ANY_CHGS, FLG_HAS_NOMINEE, FLG_HAS_OLD_LOAN, TARGET should be categorical)

loancamp$TARGET <- as.factor(loancamp$TARGET)
loancamp$FLG_HAS_CC <- as.factor(loancamp$FLG_HAS_CC)
loancamp$FLG_HAS_ANY_CHGS <- as.factor(loancamp$FLG_HAS_ANY_CHGS)
loancamp$FLG_HAS_NOMINEE <- as.factor(loancamp$FLG_HAS_NOMINEE)
loancamp$FLG_HAS_OLD_LOAN <- as.factor(loancamp$FLG_HAS_OLD_LOAN)
str(loancamp)

## check for missing values
colSums(is.na(loancamp))

#write.csv(loancamp,"loancamp.csv")
```

##Calculate baseline conversion rate
```{r}
respons_rate <- round(prop.table(table(loancamp$TARGET)),2)
respons_rate
```

## Data visualization using EDA (Univariates)

## EDA - histogram plot for important numeric variables
```{r}
library(ggplot2)
library(cowplot)

ggp1 = ggplot(data = loancamp, aes(x = AGE))+
      geom_histogram(fill = "lightblue", binwidth = 5, colour = "black")+
      geom_vline(aes(xintercept = median(AGE)), linetype = "dashed")

ggp2 = ggplot(data = loancamp, aes(x = HOLDING_PERIOD))+
      geom_histogram(fill = "lightgreen", binwidth = 5, colour = "black")+
      geom_vline(aes(xintercept = median(HOLDING_PERIOD)), linetype = "dashed")

ggp3 = ggplot(data = loancamp, aes(x = LEN_OF_RLTN_IN_MNTH))+
      geom_histogram(fill = "lightpink", binwidth = 5, colour = "black")+
      geom_vline(aes(xintercept = median(LEN_OF_RLTN_IN_MNTH)), linetype = "dashed")

ggp4 = ggplot(data = loancamp, aes(x = NO_OF_L_CR_TXNS))+
      geom_histogram(fill = "lightgray", binwidth = 5, colour = "black")+
      geom_vline(aes(xintercept = median(NO_OF_L_CR_TXNS)), linetype = "dashed")

ggp5 = ggplot(data = loancamp, aes(x = NO_OF_L_DR_TXNS))+
      geom_histogram(fill = "lightyellow", binwidth = 5, colour = "black")+
      geom_vline(aes(xintercept = median(NO_OF_L_DR_TXNS)), linetype = "dashed")

plot_grid(ggp1, ggp2, ggp3, ggp4, ggp5, labels = "AUTO")

```

## EDA - bar plot for important numeric variables
```{r}

ggb1 = ggplot(data = loancamp, aes(y = AGE))+geom_boxplot(fill = "lightblue")
ggb2 = ggplot(data = loancamp, aes(y = HOLDING_PERIOD))+geom_boxplot(fill = "lightgreen")
ggb3 = ggplot(data = loancamp, aes(y = LEN_OF_RLTN_IN_MNTH))+geom_boxplot(fill = "lightpink")
ggb4 = ggplot(data = loancamp, aes(y = NO_OF_L_CR_TXNS))+geom_boxplot(fill = "lightgray")
ggb5 = ggplot(data = loancamp, aes(y = NO_OF_L_DR_TXNS))+geom_boxplot(fill = "lightyellow")

plot_grid(ggb1, ggb2, ggb3, ggb4, ggb5, labels = "AUTO")


```


##barplot for important categorical variables
```{r}

ggc1 = ggplot(data = loancamp, aes(x = GENDER))+geom_bar(stat = "count", width = 0.7, fill = "steelblue")
ggc2 = ggplot(data = loancamp, aes(x = OCCUPATION))+geom_bar(stat = "count", width = 0.7, fill = "steelblue")
ggc3 = ggplot(data = loancamp, aes(x = FLG_HAS_CC))+geom_bar(stat = "count", width = 0.7, fill = "steelblue")
ggc4 = ggplot(data = loancamp, aes(x = FLG_HAS_OLD_LOAN))+geom_bar(stat = "count", width = 0.7, fill = "steelblue")
plot_grid(ggc1, ggc2, ggc3, ggc4, labels = "AUTO")


```

# Bivariate analysis
## Box plot for  important numberic x variables vs TARGET
```{r}
#Age vs Target, LEN_OF_RLTN_IN_MNTH vs TARGET, HOLDING_PERIOD vs TARGET
ggbi1 = ggplot(data = loancamp, aes(x = TARGET, y = AGE, fill = TARGET))+geom_boxplot()
ggbi2 = ggplot(data = loancamp, aes(x = TARGET, y = LEN_OF_RLTN_IN_MNTH, fill = TARGET))+geom_boxplot()
ggbi3 = ggplot(data = loancamp, aes(x = TARGET, y = HOLDING_PERIOD, fill = TARGET))+geom_boxplot()
plot_grid(ggbi1, ggbi2, ggbi3, labels = "AUTO")


```



```{r}
str(loancamp)
```


##stacked barplot for important categorical x variables vs TARGET
```{r}
## GENDER, OCCUPATION, ACC_TYPE, FLG_HAS_CC, FLG_HAS_ANY_CHGS, ##FLG_HAS_OLD_LOAN


ggcd1 = ggplot(data = loancamp, aes(x = GENDER, y = as.numeric(TARGET),  fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd1

ggcd2 = ggplot(data = loancamp, aes(x = OCCUPATION, y = as.numeric(TARGET), fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd2 + theme(legend.position = "none")

ggcd3 = ggplot(data = loancamp, aes(x = ACC_TYPE, y = as.numeric(TARGET), fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd3 + theme(legend.position = "none")

ggcd4 = ggplot(data = loancamp, aes(x = FLG_HAS_CC, y = as.numeric(TARGET), fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd4 + theme(legend.position = "none")

ggcd5 = ggplot(data = loancamp, aes(x = FLG_HAS_ANY_CHGS, y = as.numeric(TARGET), fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd5 + theme(legend.position = "none")


ggcd6 = ggplot(data = loancamp, aes(x = FLG_HAS_OLD_LOAN, y = as.numeric(TARGET), fill = TARGET)) + geom_bar(stat = "identity", position = "fill")
ggcd6 + theme(legend.position = "none")


plot_grid(ggcd1, ggcd2, ggcd3, ggcd4, ggcd5, ggcd6)+ theme(legend.position = "best")


```




#split dataset into development (train) and holdout (validation) sets
```{r}
library(caTools)

set.seed(123)

split = sample.split(loancamp$TARGET, SplitRatio = 0.7)
devdata = subset(loancamp, split == TRUE)
holddata = subset(loancamp, split == FALSE)

## Check if distribution of partition data is correct for the develmnt dataset
prop.table(table(devdata$TARGET))
prop.table(table(holddata$TARGET))

dim(devdata)
dim(holddata)
names(devdata)
```



#Build the Logistic Regression Model
```{r}
library(glmnet)
devdataorg = devdata
holddataorg = holddata
names(devdataorg)

#Remove NO_OF_CHQ_DR_TXNS and AMT_L_DR as they show no value in Log Reg output
devdata = devdata[-c(17,24)]
holddata = holddata[-c(17,24)]
colnames(devdata)
colnames(holddata)
logreg = glm(TARGET ~., data=devdata, family="binomial")
summary(logreg)
```



#McFadden or psuedo R2 interpretation
```{r}
#install.packages("pscl")
library(pscl)

pR2(logreg)
```

#Check for VIF
```{r}
library(car)
vif(logreg)
```



#based on VIF results, remove x variables with VIF above 4 in the
#datasets (NO_OF_L_DR_TXNS, AMT_MOB_DR, AVG_AMT_PER_MOB_TXN, NO_OF_L_CR_TXNS, #NO_OF_ATM_DR_TXNS)
```{r}
names(devdata)
devdata1 = devdata[,-c(11, 22, 32, 10, 14)]

names(holddata)
holddata1 = holddata[,-c(11, 22, 32, 10, 14)]
names(devdata1)
names(holddata1)
```

#Build the Logistic Regression Model
```{r}
logreg1 = glm(TARGET ~., data=devdata1, family="binomial")
#summary(logreg1)
```

#check for VIF again
```{r}
vif(logreg1)
```


# test overall significance of the model

```{r}
#install.packages("lmtest")
library(lmtest)

lrtest(logreg1)
```


```{r}
library(pscl)
pR2(logreg1)
```

#individual coeff significance check
```{r}
summary(logreg1)
```


##predict for train dataset
```{r}
devdata1.predict.score=predict(logreg1,newdata = devdata1, type="response")

## Assgining 0 / 1 class based on certain threshold
devdata1$Class = ifelse(devdata1.predict.score>0.10,1,0)


## Creating the confusion matrix
tabdev=with(devdata1, table(TARGET,Class))

tabdev

```

# calculate accuracy for train dataset
```{r}
train_accuracy = round((tabdev[1,1]+tabdev[2,2])/(tabdev[1,1]+tabdev[2,2]+tabdev[2,1]+tabdev[1,2]),2)

train_sensitivity = tabdev[2,2] / (tabdev[2,1]+tabdev[2,2])

specificity = tabdev[1,1]/(tabdev[1,1]+tabdev[1,2])

train_accuracy
train_sensitivity
specificity
```


##predict for test dataset
```{r}
holddata1.predict.score=predict(logreg1,newdata = holddata1, type="response")
hist(holddata1.predict.score, main = "Histogram of predicted probabilities")
```


##Predict for the development set
```{r}


## Assgining 0 / 1 class based on certain threshold
holddata1$Class = ifelse(holddata1.predict.score>0.10,1,0)


## Creating the confusion matrix
tabtest=with(holddata1, table(TARGET,Class))

tabtest
```


```{r}
test_accuracy = round((tabtest[1,1]+tabtest[2,2])/(tabtest[1,1]+tabtest[2,2]+tabtest[2,1]+tabtest[1,2]),2)

test_sensitivity = tabtest[2,2] / (tabtest[2,1]+tabtest[2,2])

test_specificity = tabtest[1,1]/(tabtest[1,1]+tabtest[1,2])

test_accuracy
test_sensitivity
test_specificity
```

